Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-16 paper/ms.tex
manuscript: UTF-8 insanity

\added{The authors thank K.~Anderson for fruitful discussions, and are
also grateful to the anonymous referee for their constructive comments
and suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%

The ASTEP project acknowledges support from the French and Italian
Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d’Azur
under Idex UCAJEDI (ANR-15-IDEX-01). We thank the dedicated staff at
Concordia for their continuous presence and support throughout the
Austral winter.
%
This research received funding from the European Research Council
(ERC) under the European Union's Horizon 2020 research and innovation
programme (grant n$^\circ$ 803193/BEBOP), and from the
Science and Technology Facilities Council (STFC; grant n$^\circ$
ST/S00193X/1).
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

This research was based in part on observations obtained at the
Southern Astrophysical Research (SOAR) telescope, which is a joint
project of the Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e
Inova\c{c}\~{o}es (MCTI/LNA) do Brasil, the US National Science
Foundation’s NOIRLab, the University of North Carolina at Chapel Hill
(UNC), and Michigan State University (MSU).

>>>>

\added{The authors thank K.~Anderson for fruitful discussions, and are
also grateful to the anonymous referee for their constructive comments
and suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%

The ASTEP project acknowledges support from the French and Italian
Polar Agencies, IPEV and PNRA, and from Universit\'e C\^ote d'Azur
under Idex UCAJEDI (ANR-15-IDEX-01). We thank the dedicated staff at
Concordia for their continuous presence and support throughout the
Austral winter.
%
This research received funding from the European Research Council
(ERC) under the European Union's Horizon 2020 research and innovation
programme (grant n$^\circ$ 803193/BEBOP), and from the
Science and Technology Facilities Council (STFC; grant n$^\circ$
ST/S00193X/1).
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

This research was based in part on observations obtained at the
Southern Astrophysical Research (SOAR) telescope, which is a joint
project of the Minist\'{e}rio da Ci\^{e}ncia, Tecnologia e
Inova\c{c}\~{o}es (MCTI/LNA) do Brasil, the US National Science
Foundation's NOIRLab, the University of North Carolina at Chapel Hill
(UNC), and Michigan State University (MSU).
